Describing vocalizations in young children: A big data approach through citizen science annotation

### 2020-11-17 202010_jslhr/lena-ana/add-lena-ana.Rmd
almost ready to submit

```{r read-data,eval=F}
read.csv("../Derived_Data/result_final_lisa.csv")->metadata
metadata[1,]

@@

  } else print(paste(thisits,"not found"))
}
write.csv(all_segments,"../Derived_Data/LENA_type_lab.csv",row.names = F)
```

@@

read.csv("../Derived_Data/LENA_type_lab.csv")->all_segments

>>>>

NOTE: This section cannot be reproduced because it requires access to data that haven't been shared.

```{r read-data,eval=F}
read.csv("result_final_lisa.csv")->metadata
metadata[1,]

@@

  } else print(paste(thisits,"not found"))
}
write.csv(all_segments,"LENA_type_lab.csv",row.names = F)
```

@@

read.csv("LENA_type_lab.csv")->all_segments

### 2020-11-17 202010_jslhr/paper.Rmd
almost ready to submit

# type: speech; areas of interest: assessment, infants, meta-analyses, prevention, speech recognition, screening, language, early intervention, cultural and ling diversity, dev lang disorders, autism, bilingualism --> choose 5: infants, prevention, dev lang disorders, early interv, diagnostics
# Clinical practice research that evaluates methods of prevention, screening, diagnosis, treatment or models of service delivery that may improve the function and quality of life for individuals with or at risk of developing disorders of speech, language, cognition, swallowing, audition, and/or balance.
# #up to 3 keywords
# keywords          : " reliability; validation; daylong audiorecordings"
# wordcount         : "7,113"

@@

figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : yes

@@

class             : "man"
output            : papaja::apa6_pdf

@@

data_ang <- read.csv("../Derived_Data/classifications_PU_zoon_final17.csv",header=T,sep=",")
data_td <- read.csv("../Derived_Data/classifications_PU_zoon_final.csv")
data_all<-rbind(data_ang, data_td)

@@

demo_data=read.csv("../Derived_Data/demo-data.tsv",sep="\t")
#add filenames to demo data, to be used later
demo_data_fn <- demo_data %>% 
     left_join(select(data_all, filename, ChildID), by = c("ChildID"))
demo_data_fn<-unique(demo_data_fn)

@@

kable(tab1,cap=mycaption, col.names = NULL)%>%
  collapse_rows(columns = 1:6, valign = "middle") %>%
add_header_above(c(" " = 1, "Recall"= 3, "Label Frequency" = 2))
```

@@

```{r bychunk-age, echo=F}
read.csv("../Derived_Data/chunk_majority_agreement_1751.csv")->chunk
bychild=table(chunk$Answer,chunk$ChildID)
cans=bychild["Canonical",]
noncans=bychild["Non-Canonical",]
Junk=bychild["Junk",]
sum_bychild=table(chunk$ChildID)

@@

We are grateful to ...

MOVE FIGURE 1 HERE

MOVE FIGURE 2 HERE

etc

>>>>

# type: speech; areas of interest: assessment, infants, meta-analyses, prevention, speech recognition, screening, language, early intervention, cultural and ling diversity, dev lang disorders, autism, bilingualism --> choose 5: infants, prevention, dev lang disorders, early interv, diagnostics
# Clinical practice research that evaluates methods of prevention, screening, diagnosis, treatment or models of service delivery that may improve the function and quality of life for individuals with or at risk of developing disorders of speech, language, cognition, swallowing, audition, and/or balance.
# #up to 3 keywords
# keywords          : "reliability; validation; daylong audiorecordings"
# wordcount         : "7,113"

@@

figsintext        : no
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : yes

@@

class             : "man"
output            : papaja::apa6_word

@@

data_ang <- read.csv("segment_AS.csv",header=T,sep=",")
data_td <- read.csv("segment_LRC.csv")
data_all<-rbind(data_ang, data_td)

@@

demo_data=read.csv("demo-data.tsv",sep="\t")
#add filenames to demo data, to be used later
demo_data_fn <- demo_data %>% 
     left_join(select(data_all, filename, ChildID), by = c("ChildID"))
demo_data_fn<-unique(demo_data_fn)

@@

kable(tab1,cap=mycaption, col.names = NULL) %>%
  collapse_rows(columns = 1:6, valign = "middle") #%>%
#add_header_above(c(" " = 1, "Recall"= 3, "Label Frequency" = 2))
```

@@

```{r bychunk-age, echo=F}
read.csv("zoo_chunk_majority_agreement.csv")->chunk
bychild=table(chunk$Answer,chunk$ChildID)
cans=bychild["Canonical",]
noncans=bychild["Non-Canonical",]
Junk=bychild["Junk",]
sum_bychild=table(chunk$ChildID)

@@

We are grateful to the families who contributed their data; to the Zooniverse volunteers that made this work possible; and the audience and technical committee of SLT 2020 for helpful feedback on preliminary analyses.

### 2020-11-17 202010_jslhr/paper.tex
almost ready to submit

\PassOptionsToPackage{unicode=true}{hyperref} % options for packages loaded elsewhere
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[english,,man,floatsintext]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provides euro and other symbols
\else % if luatex or xelatex
  \usepackage{unicode-math}
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage[]{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\usepackage{hyperref}
\hypersetup{
            pdftitle={Describing vocalizations in young children: A big data approach through citizen science annotation},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}

@@

Correspondence concerning this article should be addressed to Alejandrina Cristia, 29 rue d'Ulm, 75005, Paris, France. E-mail: alecristia@gmail.com}
\usepackage{lineno}

@@

Next, we looked at whether having more segments from each child may lead to more reliable metrics. We observed a non-significant trend {[}t(17.88)=348.70 and 375.50{]} for lower number of segments in the Angelman syndrome group (mean 348.70, range 163-599) than among low-risk control infants (mean 375.50, range 224-627), likely because of the lower volubility of the former children. Moreover, these numbers of segments are much larger than those used in previous work relying on citizen science classifications (Cychosz et al., 2019). We therefore asked whether the correlations between laboratory and Zooniverse child-level estimates are affected by how much data is extracted from each child by sampling 100 segments from all children (following Cychosz et al., 2019). We randomly sampled 100 segments from each child's data, and recalculated the linguistic and Canonical Proportions based only on these associated judgments. We repeated this process 50 times, to assess the extent to which the association between laboratory- and Zooniverse-derived metrics varied in each random sample. The mean correlations across 50 runs were lower than those recovered using all segments from each child (see Table 2), particularly for the low-risk younger infants, and for Linguistic Proportion. This may indicate that, particularly in some groups of infants, 100 segments may not be sufficient to capture a stable estimate of the child's Linguistic and Canonical Proportions. We also observed quite a bit of variance across the 50 runs. For Linguistic Proportion, the range of correlations found for all infants was {[}0.51,0.91{]}; for the Angelman syndrome group {[}0.60,0.96{]}; for the low-risk group {[}0.05,0.96{]}. For Canonical Proportion, the range of correlations found for all infants was {[}0.82,0.96{]}; for the Angelman syndrome group {[}0.59,0.95{]}; for the low-risk group {[}0.77,0.98{]}.

@@

\caption{\label{tab:tab-cors}Pearson correlation coefficients across metrics derived from laboratory and Zooniverse annotations in the Angelman syndrome (AS) group data, low-risk (LR) group data, or for all children together (all) in three ways. First, All seg indicates that Zooniverse annotations at the clip level were first combined at the segment level. Second, Chunks indicates that they were analyzed directly at the clip level. Both of these are based on all the data. Third, rows labeled 100 seg indicate that laboratory- and Zooniverse-derived metrics were based on only 100 segments (median over 50 runs in which 100 segments were randomly selected from each child).}
\centering
\begin{tabular}[t]{l|r|r}
\hline
  & Linguistic Proportion & Canonical Proportion\\
\hline
All seg AS & 0.878 & 0.681\\
\hline
Chunks AS & 0.845 & 0.724\\
\hline
100 seg AS & 0.855 & 0.809\\
\hline
All seg LR & 0.828 & 0.984\\
\hline
Chunks LR & 0.794 & 0.972\\
\hline
100 seg LR & 0.609 & 0.907\\
\hline
All seg all & 0.794 & 0.920\\
\hline
Chunks all & 0.798 & 0.949\\
\hline
100 seg all & 0.761 & 0.889\\
\hline
\end{tabular}
\end{table}

>>>>

\PassOptionsToPackage{unicode=true}{hyperref} % options for packages loaded elsewhere
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[english,,man]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provides euro and other symbols
\else % if luatex or xelatex
  \usepackage{unicode-math}
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage[]{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\usepackage{hyperref}
\hypersetup{
            pdftitle={Describing vocalizations in young children: A big data approach through citizen science annotation},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}

@@

Correspondence concerning this article should be addressed to Alejandrina Cristia, 29 rue d'Ulm, 75005, Paris, France. E-mail: alecristia@gmail.com}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{lineno}

@@

Next, we looked at whether having more segments from each child may lead to more reliable metrics. We observed a non-significant trend {[}t(17.88)=348.70 and 375.50{]} for lower number of segments in the Angelman syndrome group (mean 348.70, range 163-599) than among low-risk control infants (mean 375.50, range 224-627), likely because of the lower volubility of the former children. Moreover, these numbers of segments are much larger than those used in previous work relying on citizen science classifications (Cychosz et al., 2019). We therefore asked whether the correlations between laboratory and Zooniverse child-level estimates are affected by how much data is extracted from each child by sampling 100 segments from all children (following Cychosz et al., 2019). We randomly sampled 100 segments from each child's data, and recalculated the linguistic and Canonical Proportions based only on these associated judgments. We repeated this process 50 times, to assess the extent to which the association between laboratory- and Zooniverse-derived metrics varied in each random sample. The mean correlations across 50 runs were lower than those recovered using all segments from each child (see Table 2), particularly for the low-risk younger infants, and for Linguistic Proportion. This may indicate that, particularly in some groups of infants, 100 segments may not be sufficient to capture a stable estimate of the child's Linguistic and Canonical Proportions. We also observed quite a bit of variance across the 50 runs. For Linguistic Proportion, the range of correlations found for all infants was {[}0.44,0.89{]}; for the Angelman syndrome group {[}0.49,0.97{]}; for the low-risk group {[}0.29,0.99{]}. For Canonical Proportion, the range of correlations found for all infants was {[}0.75,0.94{]}; for the Angelman syndrome group {[}0.79,0.99{]}; for the low-risk group {[}0.55,0.94{]}.

@@

\caption{\label{tab:tab-cors}Pearson correlation coefficients across metrics derived from laboratory and Zooniverse annotations in the Angelman syndrome (AS) group data, low-risk (LR) group data, or for all children together (all) in three ways. First, All seg indicates that Zooniverse annotations at the clip level were first combined at the segment level. Second, Chunks indicates that they were analyzed directly at the clip level. Both of these are based on all the data. Third, rows labeled 100 seg indicate that laboratory- and Zooniverse-derived metrics were based on only 100 segments (median over 50 runs in which 100 segments were randomly selected from each child).}
\centering
\begin{tabular}[t]{l|r|r}
\hline
  & Linguistic Proportion & Canonical Proportion\\
\hline
All seg AS & 0.878 & 0.681\\
\hline
Chunks AS & 0.845 & 0.724\\
\hline
100 seg AS & 0.770 & 0.912\\
\hline
All seg LR & 0.828 & 0.984\\
\hline
Chunks LR & 0.794 & 0.972\\
\hline
100 seg LR & 0.841 & 0.808\\
\hline
All seg all & 0.794 & 0.920\\
\hline
Chunks all & 0.798 & 0.949\\
\hline
100 seg all & 0.719 & 0.873\\
\hline
\end{tabular}
\end{table}
